Evaluating Perceptual Judgements on 3D Printed Bar Charts

### 2024-01-22 jds.rmd
Corrected graph axis label

res %>%
  filter(plot == "3dDigital") %>%
  ggplot(aes(x = plot3dClicks, y = response)) + geom_point() + 
  xlab("# Clicks on WebGL Plot") + ylab("Count") + ggtitle("Accuracy and Participant Interactivity") + 
  geom_smooth(method = "lm", se = T) + 
  theme_bw()
```

>>>>

res %>%
  filter(plot == "3dDigital") %>%
  ggplot(aes(x = plot3dClicks, y = response)) + geom_point() + 
  xlab("# Clicks on WebGL Plot") + ylab("Log Error") + ggtitle("Accuracy and Participant Interactivity") + 
  geom_smooth(method = "lm", se = T) + 
  theme_bw()
```
